Local Group Satellite Distributions in the Illustris Simulation

### 2017-10-20 paper/paper.tex
new plots

\begin{figure*}
\centering
\includegraphics[width=0.35\textwidth]{LG_scatter_mu.pdf}
\includegraphics[width=0.35\textwidth]{LG_scatter_width.pdf}
\includegraphics[width=0.35\textwidth]{LG_scatter_ca_ratio.pdf}
\includegraphics[width=0.35\textwidth]{LG_scatter_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_scatter}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.35\textwidth]{distribution_random_mu.pdf}
\includegraphics[width=0.35\textwidth]{distribution_random_width.pdf}
\includegraphics[width=0.35\textwidth]{distribution_random_ca_ratio.pdf}
\includegraphics[width=0.35\textwidth]{distribution_random_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_distribution}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{scatter_mu.pdf}
\includegraphics[width=0.7\textwidth]{scatter_width.pdf}
\includegraphics[width=0.7\textwidth]{scatter_ca_ratio.pdf}
\includegraphics[width=0.7\textwidth]{scatter_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{distribution_mu.pdf}
\includegraphics[width=0.7\textwidth]{distribution_width.pdf}
\includegraphics[width=0.7\textwidth]{distribution_ca_ratio.pdf}
\includegraphics[width=0.7\textwidth]{distribution_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{scatter_random_ranked_width.pdf}
\includegraphics[width=0.45\textwidth]{scatter_ranked_width.pdf}
\includegraphics[width=0.45\textwidth]{scatter_norm_width.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_scatter}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{scatter_random_ranked_ca_ratio.pdf}
\includegraphics[width=0.45\textwidth]{scatter_ranked_ca_ratio.pdf}
\includegraphics[width=0.45\textwidth]{scatter_norm_ca_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_scatter}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{scatter_random_ranked_ba_ratio.pdf}
\includegraphics[width=0.45\textwidth]{scatter_ranked_ba_ratio.pdf}
\includegraphics[width=0.45\textwidth]{scatter_norm_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_scatter}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{scatter_random_ranked_mu.pdf}
\includegraphics[width=0.45\textwidth]{scatter_ranked_mu.pdf}
\includegraphics[width=0.45\textwidth]{scatter_norm_mu.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_scatter}}
\end{figure}
